### 2024-10-21 mycv/subs/papers.tex
update
updates in the list of my papers in preparation
snapshot

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------

@@

  {Jos\'{e} Victoria-Hern\'{a}ndez$^*$, \underline{Y. Jeong}$^*$, Dietmar Letzig}
  {Deformation mechanisms of Mg-ZEWK2000 alloy at RT and 225°C studied by slip trace analysis and interpreted via crystal plasticity simulations}
  {in preparation}

@@

@@

  {A critical discussion of elasto-visco-plastic self-consistent (EVPSC) models}
  {in preparation}

@@

  {in-press}

>>>>

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % % ---------------------------------------------------------
  % \cventry
  % {Jos\'{e} Victoria-Hern\'{a}ndez$^*$, \underline{Y. Jeong}$^*$, Dietmar Letzig}
  % {Deformation mechanisms of Mg-ZEWK2000 alloy at RT and 225°C studied by slip trace analysis and interpreted via crystal plasticity simulations}
  % {in preparation}
  % {}
  % {
  % }

@@

  {\href{https://dx.doi.org/10.2139/ssrn.4969819)}{A critical discussion of elasto-visco-plastic self-consistent (EVPSC) models}}
  {submitted}

@@

    %% % ---------------------------------------------------------

@@

  {Iftekhar A. Riyad, Bjorn Clausen, Daniel J. Savage, \underline{Y. Jeong}, Donald W. Brown, Mark Knezevic}
  {Modeling deformation, recovery, and recrystallization of tantalum using a higher order elasto-viscoplastic self-consistent model}
  {submitted}

@@

  {Vol. 12 (8), 3409-3430, 2024}
